Comments on binomial graph learning

### 2022-04-13 model specification.Rmd
add model specification

## Method of Estimation
### Conditional likelihood for one stratum
Let $O_i$ denote the set of nodes at stratum $i$ that have observed signals of 1, and let $Z_i$ denote the set of nodes at stratum $i$ that have observed signals of 0. Suppose the number of nodes that have signals of 1 at stratum $i$ is $k_i$. The conditional likelihood function based on model (\ref{eq:binaryglm}) for one stratum $i$ of size $N$, is

\begin{equation}
	\label{eq:stratumlikelihood}
	\begin{aligned}
	&	P(Y_{il} = 1 \text{ for } l \in O_i, Y_{im} = 0 \text{ for } m \in Z_i | \sum_{j=1}^M Y_{ij} = k_i) \\   
	& =  {\text{exp} (\sum_{l \in O_i}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_i}^M} \text{exp} (\sum_{j \in J}\mathbf{A}[j, ] h  },
	\end{aligned}
\end{equation}

where $C_{k_i}^M$ is the set of all subsets of size $k_i$ of the set ${1, 2, \dots, M}$.

@@

<!-- \begin{equation} -->
<!-- 	\label{eq:condloglikelihood} -->
<!-- 	\begin{aligned} -->
<!-- 	&	P(Y_{il} = 1 \text{ for } l \in O_i, Y_{im} = 0 \text{ for } m \in Z_i | \sum_{j=1}^M Y_{ij} = k_i) \\    -->
<!-- 	& =  {\text{exp} (\sum_{l \in O_i}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_i}^M} \text{exp} (\sum_{j \in J}\mathbf{A}[j, ] h  }, -->
<!-- 	\end{aligned} -->
<!-- \end{equation} -->

>>>>

## Method of Estimation
### Conditional likelihood for one stratum
Let $O_j$ denote the set of nodes at stratum $j$ that have observed signals of 1, and let $Z_j$ denote the set of nodes at stratum $j$ that have observed signals of 0. Suppose the number of nodes that have signals of 1 at stratum $j$ is $k_j$. The conditional likelihood function based on model (\ref{eq:binaryglm}) for stratum $j$ of size $N$, is

\begin{equation}
	\label{eq:stratumlikelihood}
	\begin{aligned}
	&	P(Y_{lj} = 1 \text{ for } l \in O_j, Y_{mj} = 0 \text{ for } m \in Z_j | \sum_{i=1}^N Y_{ij} = k_j) \\   
	& =  {\text{exp} (\sum_{l \in O_j}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) },
	\end{aligned}
\end{equation}

where $C_{k_j}^N$ is the set of all subsets of size $k_j$ of the set ${1, 2, \dots, N}$.

### Conditional likelihoood function
The conditional likelihood function for all strata is written as
\begin{equation}
	\label{eq:conlikelihood}
	\begin{aligned}
	&	L(\mathbf{A}, \beta)  = \prod_{j=1}^M {\text{exp} (\sum_{l \in O_j}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) },
	\end{aligned}
\end{equation}

@@

\begin{equation}
	\label{eq:condloglikelihood}
	\begin{aligned}
	&	\text{log}(L(\mathbf{A}, \beta))  = \sum_{j=1}^M \sum_{l \in O_j}\mathbf{A}[l, ] h  - \sum_{j=1}^M \text{log}\sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) ,
	\end{aligned}
\end{equation}
